# Results

## Packages

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(geojsonio)
library(sp)
#for pcp
library(hrbrthemes)
library(GGally)
library(viridis)
json_map <- geojson_read("https://raw.githubusercontent.com/alexjalali/remotelearningedav/main/School%20Districts.geojson", what = "sp")

df <- read.csv(file='./datasets/DataClean.csv')
df_total <- subset(df, Category == "total") #dataframe with just aggregates
```

## Try 1

```{r}
ggplot(data = df_total, aes(y = MathScores2019, x = District)) +
  geom_point() + xlab("District") + ylab("Average Math Scores in 2019") + ggtitle("Math scores by district") +
  scale_x_continuous(breaks = seq(1, 32, 1))
```

## Plot from JSON

```{r}
plot(json_map, col = "grey")
```
## <span style="color:darksalmon"> Section 1: Remote Learning Preferences for different districts </span>
### <span style="color:darksalmon"> 1.Normal bar plot of remote learning preferences </span>
```{r}
p1 <- ggplot(df_total, aes(PercentRemote)) +
  geom_histogram(binwidth = 5, boundary = 60,
                 fill = "lightBlue", col = "black") +
  xlab("% Remote")+
  ggtitle("Histogram of Percent of Students who Prefer Remote Learning per District")
```


```{r}
p1
```
### <span style="color:darksalmon"> 2.Cleveland dot plot of remote learning preferences per district (Order by Highest to Lowest) </span>
```{r}
district_remover_per_reorder <- fct_reorder(as.character(df_total$District), df_total$PercentRemote, min)

p2 <- ggplot(df_total, aes(PercentRemote,district_remover_per_reorder)) +
  geom_point(color = "darksalmon") +
  xlab("% Remote")+
  ylab("District")+theme_linedraw()+
  ggtitle("Cleveland dot plot of Percent of Students who Prefer Remote Learning per District")
p2
```

## <span style="color:darksalmon"> Section 2: Comparing same category across different districts </span>
### <span style="color:darksalmon"> Cleveland dot plot showing gender vs. remote learning AND ELL vs. remote learning </span>

```{r}
gender_plot <- df%>%filter(DisaggregationCategory == "Gender")
district_remover_per_reorder2 <- fct_reorder(as.character(gender_plot$District), gender_plot$PercentRemote, min)

p3 <- ggplot(gender_plot, aes(PercentRemote,district_remover_per_reorder2)) +
  geom_point(aes(color =Category)) + geom_line(aes(group = District),alpha=0.3) +
  xlab("% Remote")+
  ylab("District")+theme_linedraw()+
  ggtitle("Cleveland dot plot of Percent showing gender vs. remote learning per District")
p3
```

```{r}
ELL_plot <- df%>%filter(DisaggregationCategory == "English Language Learner Status")
district_remover_per_reorder3 <- fct_reorder(as.character(ELL_plot$District), ELL_plot$PercentRemote, min)

p4 <- ggplot(ELL_plot, aes(PercentRemote,district_remover_per_reorder3)) +
  geom_point(aes(color=Category)) + geom_line(aes(group = District),alpha=0.3) +
  xlab("% Remote")+
  ylab("District")+theme_linedraw()+
  ggtitle("Cleveland dot plot of Percent showing ELL vs. remote learning per District")
p4
```

### <span style="color:darksalmon"> TWO Cleveland dot plot with facets showing ethnicity AND grade </span>

```{r}

Ethnicity_plot <- df%>%filter(DisaggregationCategory == "Race or Ethnicity")
district_remover_per_reorder3 <- fct_reorder(as.character(ELL_plot$District), ELL_plot$PercentRemote, min)

p4 <- ggplot(ELL_plot, aes(PercentRemote,district_remover_per_reorder3)) +
  geom_point(aes(color=Category)) + geom_line(aes(group = District),alpha=0.3) +
  xlab("% Remote")+
  ylab("District")+theme_linedraw()+
  ggtitle("Cleveland dot plot of Percent showing ELL vs. remote learning per District")
p4



ggplot(USStates, aes(x = IQ, y = reorder(State, IQ))) +
  geom_point(color = "blue") +
  facet_grid(Pres2008 ~ ., scales = "free_y", space = "free_y") +
  ggtitle('IQ of US state residents facet by Pres2008') +
  xlab("IQ") +
  ylab('') +
  theme_linedraw() +
  theme(panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank())

```

### Parallel coordinates plot

```{r pcp}
#this isn't working i am going to work on this tomorrow
#highlight the clusters based on the Species column
pcpdf <- df_total %>% subset(select=c("ELAScores2019","ELAScores2022","MathScores2019","MathScores2022","remote_cat")) 

#highlight the clusters based on the remote categorical column
pcp<-ggparcoord(pcpdf, columns=1:4, groupColumn = 5, title = "Parallel Coordiantes Plot for average test scores per district, grouped by percent remote",scale = "globalminmax") 
pcp
```
### Parallel coordinates plot

```{r}

```
